Stage-Splitting a Modal Language

### 2014-09-08 paper/semantics.tex
commented out some duplicate stuff

\begin{remark}
For any $\colone{e}{A}$ containing no $\next$ subexpressions, $\redonesym$ will
always compute an empty environment, and a partial value identical to the result
of call-by-value evaluation of $e$.
%derivationally equivalent to standard call-by-value evaluation.
\end{remark}

@@

\TODO
Note somewhere how to run stage-one non-$\fut A$ terms. For example, a stage-one
integer term is guaranteed not to depend on the table, although one might be
produced. One may either discard the table, or evaluate everything in the table
(and terminating with the partial value iff everything in the table terminates).

>>>>

%\begin{remark}
%For any $\colone{e}{A}$ containing no $\next$ subexpressions, $\redonesym$ will
%always compute an empty environment, and a partial value identical to the result
%of call-by-value evaluation of $e$.
%%derivationally equivalent to standard call-by-value evaluation.
%\end{remark}

@@

%\TODO
%Note somewhere how to run stage-one non-$\fut A$ terms. For example, a stage-one
%integer term is guaranteed not to depend on the table, although one might be
%produced. One may either discard the table, or evaluate everything in the table
%(and terminating with the partial value iff everything in the table terminates).
